Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-21 draft/chicago-spatial-covid-draft.tex
Updated dynamics section
Fixed parameter table

Immediately we see there are infinitely many non-isolated fixed points of the form $(S,0)$.
Linearizing, we get
\begin{equation*}
	\mathbf{A}_{(S,0)} = \begin{bmatrix} 0 & - \tilde{\beta} S \\ 0 & \beta S - \gamma \end{bmatrix}
\end{equation*}
Thus, as seen in Figure \ref{fig:localdyn}, for $S < \frac{\gamma}{\tilde{\beta}}$ the nodes are stable, and for $S > \frac{\gamma}{\tilde{\beta}}$ they are unstable.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.25\textwidth]{local_dynamics}
	\caption{Stream plot for the local ODE dynamics.}
	\label{fig:localdyn}
\end{figure}
We can then conclude that an epidemic will occur only if $S_0 = S(t=0) > \frac{\gamma}{\tilde{\beta}}$ \cite{Wang_SIR}.
Hence, a transcritical bifurcation occurs at $\Ro = \tilde{\beta} S_0 / \gamma$, which is known as the \textit{basic reproduction number}.

@@

\begin{savenotes}
\begin{table}[h]
	\centering
	\caption{ODE parameters}
	\label{tab:parameters}
	\begin{tabular}{ c c c c }
		\hline
		\hline
			&	&	Optimal	&	Initial value \\
		\hline
		Population	&	$N$	&	2,695,598 \\
		Initial population	&	$I_0$	&	200 \\
		Transmission rate, $S \rightarrow I$ [per day]	&	$\beta$\footnote{The transmission rate $\beta$ must be divided by $N$ when used in the ODE model.}	&	0.30	&	$c \in U[0,1]$ \\
		Transition rate, $I \rightarrow R$ [per day]	&	$\gamma$	&	0.55	&	$c \in U[0.25,0.75]$ \\
		Diffusivity, $S$ [km$^2$/day]	&	$\D_S$	&	10	&	\\
		Diffusivity, $I$ [km$^2$/day]	&	$\D_I$	&	100	&	\\
		\hline
		\hline
	\end{tabular}
\end{table}
\end{savenotes}

>>>>

Immediately we see there are infinitely many non-isolated fixed points of the form $(S,0)$.
Linearizing, we get
\begin{equation*}
	\mathbf{A}_{(S,0)} = \begin{bmatrix} 0 & - \tilde{\beta} S \\ 0 & \beta S - \gamma \end{bmatrix}
\end{equation*}
Thus, as seen in Figure \ref{fig:localdyn}, for $S < \frac{\gamma}{\tilde{\beta}}$ the nodes are stable, and for $S > \frac{\gamma}{\tilde{\beta}}$ they are unstable.
\begin{figure}[h]
	\centering
	\includegraphics[width=0.25\textwidth]{local_dynamics}
	\caption{Stream plot for the local ODE dynamics. Note the transcritical bifurcation around $S_0 = 0.4$.}
	\label{fig:localdyn}
\end{figure}
We can then conclude that an epidemic will occur only if $S_0 = S(t=0) > \frac{\gamma}{\tilde{\beta}}$ \cite{Wang_SIR}.
Hence, a transcritical bifurcation occurs at $\Ro = \tilde{\beta} S_0 / \gamma$, which is known as the \textit{basic reproduction number},. and is used to estimate how the epidemic developed initially.

@@

\begin{savenotes}
\begin{table}[h]
	\centering
	\caption{ODE parameters}
	\label{tab:parameters}
	\begin{tabular}{ c c c c }
		\hline
		\hline
			&	&	Optimal	&	Initial value \\
		\hline
		Population	&	$N$	&	2,695,598 \\
		Initial population	&	$I_0$	&	 \\
		Transmission rate, $S \rightarrow I$ [per day]	&	$\beta$\footnote{The transmission rate $\beta$ must be divided by $N$ when used in the ODE model.}	&	&	$c \in U[0,1]$ \\
		Transition rate, $I \rightarrow R$ [per day]	&	$\gamma$	&		&	$c \in U[0.25,0.75]$ \\
		Diffusivity, $S$ [km$^2$/day]	&	$\D_S$	&	10	&	\\
		Diffusivity, $I$ [km$^2$/day]	&	$\D_I$	&	100	&	\\
		\hline
		\hline
	\end{tabular}
\end{table}
\end{savenotes}
